Remote Collection of Respiratory Samples (NACFC 2023)

### 2023-06-20 Jordana Hoppe/nacfc_2023.qmd
updated report for Jordana

```{r}
#| include: false
library(pander)
library(tidyverse)
library(caret)
library(irr)
library(gtsummary)
df <- read.csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Jordana Hoppe/Home Collection/Data_Clean/clinical.csv", na.strings = "")
surveys <- read.csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Jordana Hoppe/Home Collection/Data_Clean/surveys.csv", na.strings = "")
# Combined genotype
df$Mutation.1[df$Mutation.1 != "F508del"] <- "Other"
df$Mutation.2[df$Mutation.2 != "F508del"] <- "Other"
df$Genotype <- paste(df$Mutation.1, df$Mutation.2, sep = "/")
# Age
df$Age <- difftime(df$Date.of.clinic.culture.collection, df$Patient.DOB) / 365.25
# Combine race columns
df <- df %>%
  rowwise() %>%
  mutate(
    Race = paste(
      which(c_across(Race..choice.American.Indian.or.Alaska.Native.:
      Race..choice.Unknown.or.not.reported.) == "Checked"),
      collapse = "+"
    ),
    Race = factor(Race, levels = c("1", "5"), labels = c("American Indian or Alaska Native", "White"))
  )
# Shorten organism names
bugs = colnames(df)[grep("If.culture.was.positive..select.all.organisms.isolated...choice.",colnames(df))]
bugs <- sub("If.culture.was.positive..select.all.organisms.isolated...choice.", "", bugs)
bugs = bugs[1:16]
colnames(df) <- sub("If.culture.was.positive..select.all.organisms.isolated...choice.", "", colnames(df))
bug_names=c("Methicillin sensitive Staph aureus", 
            "Methicillin resistant Staph aureus","A. xylosoxidans", 
            "Achromobacter (not xylosoxidans)","Acinetobacter","H. influenzae", 
            "P. aeruginosa", "P. aeruginosa (mucoid)", 
            "Pseudomonas species (not aeruginosa)", "B. cepacia complex",
            "Stenotrophomonas", "Aspergillus", "Penicillium species", 
            "Sceosporium species", "M. avium complex", "M. abscessus" )
```

>>>>

```{r}
#| include: false
library(pander)
library(tidyverse)
library(caret)
library(irr)
library(gtsummary)
df <- read.csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Jordana Hoppe/Home Collection/Data_Clean/clinical_2023-06-20.csv", na.strings = "")
surveys <- read.csv("/Volumes/PEDS/RI Biostatistics Core/Shared/Shared Projects/Vigers/CF/Jordana Hoppe/Home Collection/Data_Clean/surveys_2023-06-20.csv", na.strings = "")
# Combined genotype
df$Mutation.1[df$Mutation.1 != "F508del"] <- "Other"
df$Mutation.2[df$Mutation.2 != "F508del"] <- "Other"
df$Genotype <- paste(df$Mutation.1, df$Mutation.2, sep = "/")
# Age
df$Age <- difftime(df$Date.of.clinic.culture.collection, df$Patient.DOB) / 365.25
# Combine race columns
df <- df %>%
  rowwise() %>%
  mutate(
    Race = paste(
      which(c_across(Race..choice.American.Indian.or.Alaska.Native.:
      Race..choice.Unknown.or.not.reported.) == "Checked"),
      collapse = "+"
    ),
    Race = factor(Race, levels = c("1", "5"), labels = c("American Indian or Alaska Native", "White"))
  )
# Shorten organism names
bugs = colnames(df)[grep("If.culture.was.positive..select.all.organisms.isolated...choice.",colnames(df))]
bugs <- sub("If.culture.was.positive..select.all.organisms.isolated...choice.", "", bugs)
bugs = bugs[1:16]
colnames(df) <- sub("If.culture.was.positive..select.all.organisms.isolated...choice.", "", colnames(df))
bug_names=c("Methicillin sensitive Staph aureus", 
            "Methicillin resistant Staph aureus","A. xylosoxidans", 
            "Achromobacter (not xylosoxidans)","Acinetobacter","H. influenzae", 
            "P. aeruginosa", "P. aeruginosa (mucoid)", 
            "Pseudomonas species (not aeruginosa)", "B. cepacia complex",
            "Stenotrophomonas", "Aspergillus", "Penicillium species", 
            "Sceosporium species", "M. avium complex", "M. abscessus" )
```
